Codebook
========
Codebook was generated on `r as.character(Sys.time())`.

Variable list and descriptions
------------------------------

Variable name       | Description
--------------------|---------------------------------------------------------------------------------
Subject             | The ID number of the individual performing the activity. Range: 1 to 30
ActivityNum         | The ID of the activity. Range 1 to 6.
ActivityName        | The descriptive name of the activity.
FeatureCode         | The feature code - this is the feature name from the original dataset
FeatureName         | The description of the feature - this is derived from the FeatureCode
Average             | The average measurement for the particular feature, activity and subject
------------------------------------------------------------------------------------------------------

Dataset structure
-----------------

```{r}
str(dtTidyDataset)
```

Data table key
--------------

```{r}
key(dtTidyDataset)
```

Sample data
-----------

```{r}
dtTidyDataset
```

Summary of variables
--------------------

```{r}
summary(dtTidyDataset)
```
